When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2018-02-23 paper/paper.tex
Example

\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds}

@@

This model can be extended with additional constraints. These allow more inference to be performed,
and so a solution may be found (or the lack of solution may be proven) with less search.  The
simplest example is that a pattern vertex of degree $d$ may only be mapped to a target vertex of
degree at least $d$, and so constraints can be posted which eliminate values corresponding to target
vertices of low degree from domains corresponding to pattern vertices of high degree. Richer
constraints involving neighbourhood degree sequences \citep{DBLP:journals/constraints/ZampelliDS10},
neighbourhood difference constraints \citep{DBLP:journals/ai/Solnon10}, and distances and paths
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15,DBLP:conf/lion/KotthoffMS16} are also
possible.

>>>>

\usetikzlibrary{calc, positioning}

@@

For example, in \cref{figure:cpsipexample}, we would have three variables $A$, $B$ and $C$, each of
which has a domain $\{1, 2, 3, 4, 5, 6\}$. Suppose initially we guessed the assignment $A = 1$:
inference would tell us that vertices adjacent to $A$ must be mapped to vertices adjacent to $1$,
and so the value $6$ would be eliminated from the domains of both $B$ and $C$, whilst injectivity
would eliminate $1$ from $B$ and $C$. Now suppose we then guessed $B = 2$: this would leave no
suitable values for $C$, and so we would backtrack and try a new assignment for $B$. Guessing $B =
3$ will similarly give a wipeout on $C$, but guessing $B = 4$ will leave the value $5$ in the domain
of $C$, and we could then guess $C = 5$ to obtain a complete assignment.

\begin{figure}[b]
    \centering
    \begin{tikzpicture}[scale=0.3,every node/.style={font=\footnotesize}]
        \begin{scope}
            \node[draw, circle, fill=chromaygb2, inner sep=0.5pt] (Na) at (0, 0) {\phantom{0}};
            \node[draw, circle, fill=chromaygb2, inner sep=0.5pt] (Nb) at (-120:3) {\phantom{0}};
            \node[draw, circle, fill=chromaygb2, inner sep=0.5pt] (Nc) at (-60:3) {\phantom{0}};

            \node [above = 0 of Na] {A};
            \node [below = 0 of Nb] {B};
            \node [below = 0 of Nc] {C};

            \draw [ultra thick] (Na) -- (Nb);
            \draw [ultra thick] (Nb) -- (Nc);
            \draw [ultra thick] (Nc) -- (Na);
        \end{scope}

        \begin{scope}[xshift=9cm]
            \node[draw, circle, fill=chromaygb5, inner sep=0.5pt] (N1) at (0, 0) {\phantom{0}};
            \node[draw, circle, fill=chromaygb5, inner sep=0.5pt] (N2) at (180:3) {\phantom{0}};
            \node[draw, circle, fill=chromaygb5, inner sep=0.5pt] (N3) at (0:3) {\phantom{0}};
            \node[draw, circle, fill=chromaygb5, inner sep=0.5pt] (N4) at (-120:3) {\phantom{0}};
            \node[draw, circle, fill=chromaygb5, inner sep=0.5pt] (N5) at (-60:3) {\phantom{0}};
            \node[draw, circle, fill=chromaygb5, inner sep=0.5pt] (N6) at ($(-60:3)+(3,0)$) {\phantom{0}};

            \draw [ultra thick] (N1) -- (N2);
            \draw [ultra thick] (N1) -- (N3);
            \draw [ultra thick] (N1) -- (N4);
            \draw [ultra thick] (N1) -- (N5);
            \draw [ultra thick] (N4) -- (N5);
            \draw [ultra thick] (N5) -- (N6);

            \node [above = 0 of N1] {1};
            \node [above = 0 of N2] {2};
            \node [above = 0 of N3] {3};
            \node [below = 0 of N4] {4};
            \node [below = 0 of N5] {5};
            \node [below = 0 of N6] {6};

        \end{scope}
    \end{tikzpicture}

    \caption{An example used to illustrate the simple constraint programming model for the problem:
    the pattern graph is on the left, and the target graph on the right.}
    \label{figure:cpsipexample}
\end{figure}

This model can be extended with additional constraints. These allow more inference to be performed,
and so a solution may be found (or the lack of solution may be proven) with less search.  The
simplest example is that a pattern vertex of degree $d$ may only be mapped to a target vertex of
degree at least $d$, and so constraints can be posted which eliminate values corresponding to target
vertices of low degree from domains corresponding to pattern vertices of high degree. In the example
in \cref{figure:cpsipexample}, this rule would eliminate the values $2$, $3$ and $6$ from every domain at
the top of search. Richer constraints involving neighbourhood degree sequences
\citep{DBLP:journals/constraints/ZampelliDS10}, neighbourhood difference constraints
\citep{DBLP:journals/ai/Solnon10}, and distances and paths
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15,DBLP:conf/lion/KotthoffMS16} are also
possible.
